---
title: "p8105_hw3_zw2541"
author: "Zixu_Wang"
date: "10/5/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(patchwork)
```

## Problem 1

#### Read and clean the data

```{r}
library(p8105.datasets)

data("brfss_smart2010")

brfss = brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  rename(state = locationabbr, county = locationdesc) %>% 
  filter(topic == "Overall Health") %>% 
  filter(response %in% c("Excellent", "Very good","Good", "Fair", "Poor")) %>% 
  mutate(response = factor(response, levels = c("Excellent", "Very good","Good", "Fair", "Poor")))
```

#### Using this dataset, do or answer the following:

(1) In 2002, which states were observed at 7 locations?

```{r}
brfss %>% 
  filter(year == "2002") %>% 
  group_by(state) %>% 
  summarize(n_location = n_distinct(county)) %>% 
  filter(n_location == "7")
```

In 2002, Connecticut, Florida, and North Carolina were observed at 7 locations.

(2) Make a “spaghetti plot” that shows the number of locations in each state from 2002 to 2010.

```{r}
brfss %>% 
  group_by(state,year) %>% 
  summarize(n_locations = n_distinct(county)) %>% 
  ggplot(aes(x = year, y = n_locations, color = state)) +
  geom_line() +
  labs(
        title = "Spaghetti Plot-Number of Locations in Each State from 2002 to 2010",
        y = "Number of locations",
        x = "Year") +
  theme(legend.position = "bottom",
        legend.key.width = unit(.25, 'cm')) +
  guides(color = guide_legend(ncol = 15))
```

The figure above shows the number of locations being observed in each state from 2002 to 2010. For most states, number of locations approximately keep the same during these eight years and always below 20 locations. However, the number of locations in Florida changed dramaticly from 2006 to 2008.

(3) Make a table showing, for the years 2002, 2006, and 2010, the mean and standard deviation of the proportion of "Excellent" responses across locations in NY State.

```{r}
brfss %>% 
  group_by(state, year) %>% 
  filter(year %in% c("2002", "2006", "2010"),
         state == "NY",
         response == "Excellent") %>% 
  summarize(mean_prop = mean(data_value),
            sd_prop = sd(data_value)) %>% 
  knitr::kable(digits = 3)
```

The mean and sd of the proportion of "Excellent" are approximately the same in 2002, 2006 and 2010.

(4) For each year and state, compute the average proportion in each response category (taking the average across locations in a state). Make a five-panel plot that shows, for each response category separately, the distribution of these state-level averages over time.

```{r}
brfss %>% 
  group_by(year, state, response) %>% 
  summarize(response_average = mean(data_value, na.rm = TRUE)) %>% 
  ggplot(aes(x = year, y = response_average)) +
  geom_boxplot(aes(fill = factor(year))) +
  facet_grid(.~response) +
  labs(
        title = "Five-Panel Plot-Average Proportion in Each Response Category",
        y = "Average Proportion of Each Response",
        x = "Year") +
  theme(legend.position = "bottom") +
  scale_fill_discrete(name = "Year")
```

First, we could conclude from the figures above that the mean of each response remained constent from 2002 to 2010. Second, the "Very good" response has the highest mean among this response category and the "Poor" response has the lowest. Third, the mean increases from "Poor" to "Very good", and decreases when it comes to "Excellent".

## Problem 2

#### Read and clean the data

```{r}
data(instacart)
instacart = janitor::clean_names(instacart)
skimr::skim(instacart)
```

This "instacart" dataset documents the shoppoing history of different client. From the table above, we know that there are total 1384617 observations and 15 variables. Among these 15 variables, 4 are character variables ("aisle", "department", "eval_set", "product_name"), and others are all numeric variables. The meaning of each variables are showing below:

* order_id: the id number of each order
* product_id: the id number of each product
* add_to_cart_order: the order of each product be added to the cart by a client
* reordered: whether this product has been ordered before (1 means TRUE, 0 means FALSE)
* user_id: the id number of the user
* eval_set: evaluation set
* order_number: the time of this order among the shopping history
* order_dow: the day in a week when the order has been placed(0 means Monday and 6 means Sunday)
* order_hour_of_day: the time in a day when the order has been placed
* days_since_prior_order: the days between this order and the client's previous order
* product_name: the name of the product
* aisle_id: the id number of aisle
* department_id: the id number of department
* aisle: the name of the aisle the product belongs to
* department: the name of the department

For example, user(112108) placed an order(order_id: 1) of eight products(Bulgarian Yogurt, Organic 4% Milk Fat Whole Milk Cottage Cheese, etc) at 10am on Friday. And the order is this user's fourth order.